\large \texttt{insectDisease}: programmatic access to the \textit{Ecological Database of the World's Insect Pathogens}

### 2022-06-13 manuscript/coverLetter/Letter.tex
second round revisions at ecography
updates to readme and manuscript edits

{\noindent Dear \textit{Ecology Letters} editorial board,} \vskip4pt

@@

>>>>

{\noindent Dear \textit{Ecography} editorial board,} \vskip4pt

@@

I (the lead author, as I do not mean to speak for the co-authors on this point) am honestly curious in continuing this conversation, as there is a lot of nuance here. For instance, I thought having the documentation as plain text (.Rd) files in the `man` folder would still qualify as FAIR since it is readable without having to install the package. This is a more minor point to my larger curiosity about the shifting landscape of package development, and how the tools for making packages seem to enforce a rigidity in dev and toolsets (e.g., pkgdown, etc.) outside of `devtools` (and even `devtools` is less a single package and more of a collection of packages now with a set of 19+ dependencies). What will this mean to future developers? For the future of CRAN or centralized repositories? \\
